### 2024-08-29 NN/plots_preds_latex.tex
commit

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots_preds/R2-99.23-TanhFFNN-Impedance-module.png}
    \caption{Prediction of Impedance module with TanhFFNN - R-Squared: 0.94}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{plots_preds/R2-98.65-TanhReluFFNN-conc.png}
    \caption{Prediction of conc with TanhReluFFNN epochs:50 - R-Squared: 0.99}
\end{figure}

### 2024-08-29 NN/tables/backward.tex
commit

    \begin{table*}[h]
        \centering
        \begin{tabular}{lr}
\hline
 features                                                                                                                                 &    R2 \\
\hline
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp & 77.62 \\
 Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp             & 51.9  \\
 SG Coating, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp               & 51.9  \\
 SG Coating, Temp Alk Sol, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp            & 51.9  \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp                     & 74.59 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp         & 46.26 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Dip Time Sol (s), Clay Conc, Cure Time (min), Cure Temp                 & 69.37 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Clay Conc, Cure Time (min), Cure Temp                   & 62.26 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Cure Time (min), Cure Temp            & 34.36 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Temp                  & 64.92 \\
 SG Coating, Temp Alk Sol, NaOH Wt\%, Dip Time Alk (min), pH Sol, Hydro Time (h), Dip Time Sol (s), Clay Conc, Cure Time (min)            & 62.82 \\
\hline
\end{tabular}
        \caption{Results of Backward Feature Elimination}
        \label{backward}
    \end{table*}

>>>>

\begin{longtable}{lr}
\hline
 features                        &    R2 \\
\hline
 time, flowrate, temp, init conc & 98.54 \\
 flowrate, temp, init conc       &  0.66 \\
 time, temp, init conc           & 94.34 \\
 time, flowrate, init conc       & 98.02 \\
 time, flowrate, temp            & 95.41 \\
\hline
\end{longtable}

### 2024-08-29 NN/tables/forward.tex
commit

    \begin{table*}[h]
        \centering
        \begin{tabular}{lr}
\hline
 features                                                         &     R2 \\
\hline
 pH Sol                                                           &  14.56 \\
 Hydro Time (h)                                                   &  26.4  \\
 Dip Time Sol (s)                                                 &  11.24 \\
 Clay Conc                                                        &  64.24 \\
 Cure Time (min)                                                  &   0.1  \\
 SG Coating, Clay Conc                                            &  64.93 \\
 Temp Alk Sol, Clay Conc                                          &  64.93 \\
 NaOH Wt\%, Clay Conc                                             &  64.93 \\
 Dip Time Alk (min), Clay Conc                                    &  79.07 \\
 pH Sol, Clay Conc                                                &  62.87 \\
 Hydro Time (h), Clay Conc                                        & -15.61 \\
 Dip Time Sol (s), Clay Conc                                      &  80.99 \\
 Cure Time (min), Clay Conc                                       &  74.1  \\
 Cure Temp, Clay Conc                                             &  66.68 \\
 SG Coating, Clay Conc, Dip Time Sol (s)                          &  81.03 \\
 Temp Alk Sol, Clay Conc, Dip Time Sol (s)                        &  81.03 \\
 NaOH Wt\%, Clay Conc, Dip Time Sol (s)                           &  81.03 \\
 Dip Time Alk (min), Clay Conc, Dip Time Sol (s)                  &  93.94 \\
 pH Sol, Clay Conc, Dip Time Sol (s)                              &  83.22 \\
 Hydro Time (h), Clay Conc, Dip Time Sol (s)                      &  56.92 \\
 Cure Time (min), Clay Conc, Dip Time Sol (s)                     &  60.09 \\
 Cure Temp, Clay Conc, Dip Time Sol (s)                           &  60.67 \\
 SG Coating, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)      &  85.55 \\
 Temp Alk Sol, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)    &  85.55 \\
 NaOH Wt\%, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)       &  85.55 \\
 pH Sol, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)          &  77.04 \\
 Hydro Time (h), Clay Conc, Dip Time Sol (s), Dip Time Alk (min)  &  75.85 \\
 Cure Time (min), Clay Conc, Dip Time Sol (s), Dip Time Alk (min) &  71.81 \\
 Cure Temp, Clay Conc, Dip Time Sol (s), Dip Time Alk (min)       &  63.33 \\
\hline
\end{tabular}
        \caption{Results of Forward Feature Selection for different features}
        \label{forward}
    \end{table*}

>>>>

\begin{longtable}{lr}
\hline
 features                        &    R2 \\
\hline
 time                            & 93.84 \\
 flowrate                        & -0.79 \\
 temp                            &  0.69 \\
 init conc                       &  1.47 \\
 flowrate, time                  & 95.32 \\
 temp, time                      & 93.29 \\
 init conc, time                 & 94.95 \\
 temp, time, flowrate            & 95.21 \\
 init conc, time, flowrate       & 97.84 \\
 temp, time, flowrate, init conc & 97.39 \\
\hline
\end{longtable}
